The COVID-19 Pandemic's Impact on Bullying Search Intensity with respect to Asian Population

### 2023-02-22 Outputs/Paper/paper.qmd
Update paper.qmd

Anti-Asian violence skyrocketed during the Covid-19 pandemic. The Center for the Study of Hate and Extremism published a report showing how anti-Asian hate crimes in the United States grew by 339% from 2020 to 2021 - the height of the global crisis. This increase in racism, fueled by the pandemic, occurred mainly in highly populated urban cities where the population of people of Asian descent are more predominant. For example, the percentages of Asian hate crimes in New York rose from 30% to 133% and in San Francisco from 9% to 60%. American culture pretends Asian Americans face no discrimination or racism. There are countless examples where when the U.S. was faced with an economic downturn, Asian Americans were affected. The 1982 killing of Vincent Chin in Detroit came after the 1980-1982 Detroit recession and The Page Act of 1875, America's first immigration law that banned Chinese women after the Great Panic of 1873. It's safe to assume an economic horror like the pandemic would lead to hate. It was disconcerting reading about the different hate acts that occurred, and it was clear there needed to be culturally appropriate and accessible community safety programs. From the data provided, we decided to clean it, focusing on the states with an Asian population. There has been mainstream media coverage of anti-Asian racism but little effort toward the Asian American Youth.

>>>>

It has been widely reported in the media that discrimination and overt anti-Asian racism due to the COVID-19 pandemic is on the rise. By contrast, Andrew Bacher-Hicks, The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying, illustrates how the rate of bullying incidents among high schools declined during the pandemic, and discussed how these learnings can be helpful in further reducing bullying with targetted prevention and intervention strategies (Bacher-Hicks, 2020). Their analysis uses data from Google trends on search intensity for bullying related terms; cyberbullying, school bullying and bullying, and the times of the year bullying occurs. Their research proved that search intensity for bullying related terms, and state self-reported bullying rates are strongly correlated.

This paper will use the initial analysis from Bachman-Hicks research to expand on their general findings to determine if anti-Asian bullying, more specifically, has followed the same overall declining trend among high school students across America.  We will conduct our own detailed data analysis and interpretation of their results and then design three different reproductions of their data. First, we will examine all bullying, cyberbullying, and school bullying searches in the Top 10 Asian populated states and discuss how bullying rates changed from the pre-pandemic to post pandemic. Second, we will look at the top 10 Asian populated states' frequency of school bullying searches compared to the searches across the entire nation. Finally, we will examine the same searches in the top 10 lowest Asian populated states to gain a better understanding of how the lowest Asian populated states relate to the highest in terms of bullying search intensity.

In this document, we will show that while rates of bullying have declined during the Covid-19 pandemic among high school students, they have declined less in schools located in states where people of Asian descent are the highest.
